A Visibility-Based Combinatorial Data Structure for Mobile Robots in Polygons

### 2018-05-23 final_paper/paper.tex
fixed some minor figure size and position
small edits

\begin{figure}
    \includegraphics[width=0.8\linewidth]{images/viz_graph.png}
    \centering
    \caption{The vertex visibility graph}\label{fig:vvg}
    \centering
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=0.8\linewidth]{images/partial_local_sequence.png}
    \caption{Partial local sequence for $v_0$}\label{fig:pls}
    \centering
\end{figure}

@@

\section{Bounce Visibility Diagram \label{bvd_def}}
We will now define the central structure for this paper, the
\textit{Bounce Visibility Diagram} for polygon $P$. We will first insert all new
vertices from the partial local sequence for all vertices into the
polygon $P$, creating the new polygon $P'$ with $m$ vertices. Note that $P'$ is
no longer a polygon in general position.

The $x-$axis of the diagram parameterizes the boundary of the new polygon,
denoted as $\partial P'$, in counterclockwise order to $[0, m+1)$. The
enpoints of this interval are identified, though for visualization purposes we
do not represent this explicitly. We map every
point in $\partial P'$ to a point in $[0, m+1)$; vertex $v_i$ on $\partial P'$
will map to $x = i$; all points in the open edge $v_iv_{i+1}$ will uniformly map
to $(i, i+1)$. Let $f: [0, m+1)\mapsto \partial P'$ denote this
parameterization. We will generally use the variable $s$ to refer to points on
the boundary of $\partial P'$.

@@

\begin{figure}
% \makebox[\linewidth][c]{%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.5\linewidth]{images/regular_pent.png}
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.8\linewidth]{images/regular_pent_bvd.png}
\end{subfigure}
% }\\
\caption{The bounce visibility diagram for the regular pentagon. }
\label{fig:regular_pent_bvd}
\end{figure}

@@

\begin{figure}
%\hspace{-40px}
\centering
%\makebox[\linewidth][c]{%
%\hspace{30px}
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.7\linewidth]{images/chestnut_5.png}
\label{fig:t4}
\end{subfigure}
%\hspace{-40px}

\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.7\linewidth]{images/chestnut_7.png}
\label{fig:t6}
\end{subfigure}\\
\caption{The worse case polygon for $t = 4$ and $t = 6$ 
\label{fig:chestnut}}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.6\linewidth]{images/viz_graph.png}
    \centering
    \caption{The vertex visibility graph}\label{fig:vvg}
    \centering
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{images/partial_local_sequence.png}
    \caption{Partial local sequence for $v_0$}\label{fig:pls}
    \centering
\end{figure}

@@

\section{Bounce Visibility Diagram \label{bvd_def}}
We will now define the central structure for this paper, the
\textit{Bounce Visibility Diagram} for polygon $P$. We will first insert all new
vertices from the partial local sequence for all vertices into the
polygon $P$, creating the new polygon $P'$ with $m$ vertices. Each of these new
vertices marks a combinatorial change in the visibility polygon at the boundary
of the polygon as an agent traverses the boundary.

The $x-$axis of the diagram parameterizes the boundary of the new polygon,
denoted as $\partial P'$, in counterclockwise order as the interval $[0, m+1)$. The
enpoints of this interval are identified, though for visualization purposes we
do not represent this explicitly. We map every
point in $\partial P'$ to a point in $[0, m+1)$; vertex $v_i$ on $\partial P'$
will map to $x = i$; all points in the open edge $v_iv_{i+1}$ will uniformly map
to $(i, i+1)$. Let $f: [0, m+1)\mapsto \partial P'$ denote this
parameterization. We will generally use the variable $s$ to refer to points on
the boundary of $\partial P'$.

@@

\begin{figure}
% \makebox[\linewidth][c]{%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.7\linewidth]{images/regular_pent.png}
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=0.8\linewidth]{images/regular_pent_bvd.png}
\end{subfigure}
% }\\
\caption{The bounce visibility diagram for the regular pentagon. }
\label{fig:regular_pent_bvd}
\end{figure}

@@

\begin{figure}
%\hspace{-40px}
\centering
\makebox[\linewidth][c]{%
%\hspace{30px}
\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=\linewidth]{images/chestnut_5.png}
\label{fig:t4}
\end{subfigure}
%\hspace{-40px}

\begin{subfigure}{0.25\textwidth}
\centering
\includegraphics[width=\linewidth]{images/chestnut_7.png}
\label{fig:t6}
\end{subfigure}
}
\caption{The worse case polygon for $t = 4$ and $t = 6$ 
\label{fig:chestnut}}
\end{figure}
